---
title: My Google Timeline data with ` `r params$package` `      
author: |
 | Matthew Malishev  
 |  
 | @darwinanddavis  
 | 
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: blue
urlcolor: blue
citecolor: red
output:
  html_document:
    highlight: tango
    code_folding: show
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  package: "leaflet"
  dir: "/Users/malishev/Documents/Data/gggmap"
  date: !r Sys.Date()
  session: !r sessionInfo()  
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/UsefulCode
classoption: portrait
# ^['https://github.com/darwinanddavis/UsefulCode'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = F, # run all code
 echo = T, # show code chunks in output
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=T, # make output as tidy
 message = F,  # mask all messages
 warning = F, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
R version: `r params$version`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\  

R session info 

```{r, echo=F,aval=F}
params$session
```      

\newpage  

## Overview

My Google timeline data with `r params$package`.   

**Need to export as HTML, then open in internet browser.**    

### Install dependencies
```{r, load packages, include=T, cache=F, message=F, warning=F, results='hide'}
packages <- c("rgdal","dplyr","zoo","RColorBrewer","viridis","plyr","digitize","jpeg","devtools","imager","dplyr","ggplot2","ggridges","ggjoy","ggthemes","svDialogs","data.table","tibble","extrafont","sp","leaflet","htmltools")   
if (require(packages)) {
    install.packages(packages,dependencies = T)
    require(packages)
}
lapply(packages,library,character.only=T)
```


### [Gallery of map styles](https://leaflet-extras.github.io/leaflet-providers/preview/)  
\  

### Leaflet  
```{r,eval=T}
require(leaflet)

# airbnb data 
amdam <- read.csv("amdam.csv",header=T,sep=",",stringsAsFactors = T)
ll <- amdam[1,]
ll <- ll[,c("latitude","longitude")]
par(bg="black")

cleanliness <- amdam[,"review_scores_cleanliness"] %>% unique
cleanliness[is.na(cleanliness)] <- 1
beds <- amdam[,"beds"] %>% unique
beds[is.na(beds)] <- 1
beds <- beds + 1

colv <- "orange"
site_names <- paste0("Rating: ", amdam$review_scores_rating,
                      "\n\nCheck-in: ", amdam$review_scores_checkin, 
                      "\nCleanliness: ", amdam$review_scores_cleanliness,
                      "\nLocation: ", amdam$review_scores_location
                      ) 

amdam[is.na(amdam)] <- 1
  
require(leaflet)
map <- leaflet() %>% 
  setView(amdam[1,"longitude"],amdam[1,"latitude"],zoom=12) %>% 
  addTiles() %>% 
  addCircleMarkers(amdam[,"longitude"],
                   amdam[,"latitude"],
                   radius = amdam$review_scores_cleanliness/20,
                   stroke = TRUE,
                   weight = 3, 
                   opacity = 0.5,
                   color = colv,
                   fillColor = colv,
                   label=site_names,
                   popup=site_names) %>%
  addProviderTiles("CartoDB.DarkMatter")
map


```


```{r,echo=F}
require(leaflet)

amdam[is.na(amdam)] <- 1 # turn nas into 1
avail_30 <- amdam %>% dplyr::filter(amdam$availability_30 > 1) 
avail_60 <- amdam %>% dplyr::filter(amdam$availability_60 > 1) 
avail_90 <- amdam %>% dplyr::filter(amdam$availability_90 > 1) 

  
require(leaflet)
map <- leaflet() %>% 
  setView(amdam[1,"longitude"],amdam[1,"latitude"],zoom=12) %>% 
  addTiles() %>% 
  addCircleMarkers(avail_30[,"longitude"],
                   avail_30[,"latitude"],
                   radius = avail_30$review_scores_cleanliness/20,
                   stroke = TRUE,
                   weight = 3, 
                   opacity = 0.5,
                   color = "lightblue",
                   fillColor = "lightblue",
                   label=site_names,
                   popup=site_names) %>%
  addCircleMarkers(avail_60[,"longitude"],
                   avail_60[,"latitude"],
                   radius = avail_60$review_scores_cleanliness/20,
                   stroke = TRUE,
                   weight = 3, 
                   opacity = 0.5,
                   color = "pink",
                   fillColor = "pink",
                   label=site_names,
                   popup=site_names) %>% 
  addProviderTiles("CartoDB.DarkMatter")
map


```

### Interactive label options and custom tiles  

```{r, eval=T}

require(leaflet)  
require(dplyr)
require(geosphere)
require(htmltools)

setview <- c(7.369722,12.354722)
marker <- c(-26.828764,-17.009277)
mp <- data.frame(
  "name" = c("Melbourne","Atlanta"),
  "lat" = c(-37.813629,33.748997),
  "lon" = c(144.963058,-84.387985)
)
latlon_matrix <- matrix(c(mp[,"lon"],mp[,"lat"]),ncol=2)
custom_tile <- "http://a.sm.mapstack.stamen.com/(positron,(mapbox-water,$776699[hsl-color]),(buildings,$002bff[hsl-color]),(parks,$6abb9d[hsl-color]))/{z}/{x}/{y}.png"
colv <- "#4C3661"
opac <- 0.5
site_names <- mp$name
ttl <- "Debunking Flat Earth theory 101"
weblink <- "https://www.tfes.org/contact.php" # weblink
webname <- "Flat Earth Society"
href <- paste0("<b><a href=",weblink,">",webname,"</a></b>")
text_label <- "This is curved"
popup_label <- paste(sep = "<br/>",
                    "This part wraps around", paste0("@",href)
)
# label options 
marker_label_opt <- labelOptions(textsize = "20px",opacity = 0.5,offset = c(0,0))
popup_label_opt <- popupOptions(closeOnClick = F, closeButton = FALSE, textOnly = F, textsize = "2px")
text_label_opt <- labelOptions(noHide = F, direction = 'top', textOnly = F, opacity = 1,offset = c(0,0))

# title
tag.map.title <- tags$style(
  HTML(".leaflet-control.map-title { 
       transform: translate(-50%,20%);
       position: fixed !important;
       left: 50%;
       text-align: center;
       padding-left: 10px; 
       padding-right: 10px; 
       background: white; opacity: 0.7;
       font-weight: bold;
       font-size: 25px;
       }"
       ))

title <- tags$div(
  tag.map.title, HTML(ttl)
)  

# map
map <- gcIntermediate(latlon_matrix[1,],
                      latlon_matrix[2,],
                      n=100, 
                      addStartEnd=T,
                      sp=T) %>% 
  leaflet() %>% 
  setView(setview[2],setview[1],zoom=3) %>% 
  addTiles(custom_tile) %>% 
  addCircleMarkers(mp[,"lon"],
                   mp[,"lat"],
                   radius = 10,
                   stroke = TRUE,
                   weight = 3, 
                   opacity = opac,
                   color = colv,
                   fillColor = colv,
                   label=paste(site_names),
                   labelOptions = marker_label_opt
  ) %>%
  addPolylines(
    color = colv,
    opacity = opac,label = text_label, labelOptions = text_label_opt) %>% 
  addPopups(marker[2],marker[1], popup = popup_label,
            options = popup_label_opt
  ) %>% 
  addControl("@darwinanddavis", position = "topright") %>% 
  addControl(title, position = "topleft", className="map-title")
map
# save_html(map,"flatearth_2.html")


```


# Custom map tiles 

```{r}
require(leaflet)

# flat earth 
custom_tile <- "http://d.sm.mapstack.stamen.com/(positron,(parks,$3bcdd5[hsl-color]),(streets-and-labels,$e2d2f0[hsl-color]),(buildings,$e2d2f0[hsl-color]))/{z}/{x}/{y}.png"


custom_tile <- "http://d.sm.mapstack.stamen.com/((darkmatter,$00ffff[hsl-color]),(mapbox-water,$00589c[hsl-color]),(parks,$ff9a30[source-in]))/{z}/{x}/{y}.png"

# conference sites
custom_tile <- "http://c.sm.mapstack.stamen.com/(toner-lite,(mapbox-water,$000[@80]),(parks,$000[@70]),(buildings,$fabe68[hsl-color]))/{z}/{x}/{y}.png"

custom_tile <- "http://b.sm.mapstack.stamen.com/((mapbox-water,$f2f7ff[hsl-color]),(positron,$f2f7ff[hsl-color]),(buildings,$e2edff[hsl-color]),(parks,$d5e5ff[hsl-color]))/{z}/{x}/{y}.png"

custom_tile <- "http://b.sm.mapstack.stamen.com/((mapbox-water,$f2f7ff[hsl-color]),(positron,$f2f7ff[hsl-color]),(buildings,$e2edff[hsl-color]),(parks,$2c403b[hsl-color]))/{z}/{x}/{y}.png"

leaflet() %>% 
  setView(144.963058,-37.813629,zoom=12) %>% 
  addTiles(custom_tile)

```



### Flight connections maps  

```{r}
# flight connection maps  

# https://www.gis-blog.com/flight-connection-map-with-r/
# http://kateto.net/network-visualization
# https://stackoverflow.com/questions/54362265/plotting-routes-that-cross-the-international-dateline-using-leaflet-library-in-r


```


### Drawing networks of lines e.g. roads 


```{r}
# https://rpubs.com/walkerke/points_to_line
```



### Adding images within popup markers
<!-- https://stackoverflow.com/questions/32352539/plotting-barchart-in-popup-using-leaflet-library/36237460#36237460 -->  

<!-- https://stackoverflow.com/questions/36433899/image-in-r-leaflet-marker-popups -->


### Line breaks in labels and popups

```{r}
require(dplyr)
require(htmltools)
require(purrr)

long <- c(147.5, 147.5, 147.5, 147, 147)
lat <- c(-36.5, -36.5, -36.5, -36, -36)
label <- c(1, 1, 2, 1, 2)

markers <- data.frame(lat,long,label)

# label linebreak
label_breaks <- paste(
  "<strong> Lat: </strong>", markers$lat, "<br/>",
  "<strong> Lon: </strong>", markers$long, "<br/>"
) %>% map(htmltools::HTML)

# popup linebreak method 1
popup_breaks1 <- paste(sep = "<br/>",
                    "<strong> Line1: </strong>", markers$label,
                    "",
                    "<strong> Line2: </strong>", markers$label,
                    ""
)

# popup break 2 # Aggregate method
popup_breaks2 <- aggregate(label ~ lat + long, markers, paste, collapse = "<br/>")



# Markers with all of the labels
leaflet() %>%
  addTiles() %>%  
  addMarkers(lng=markers$long, lat= markers$lat, 
             label=label_breaks,
             popup= popup_breaks2
  )
```


### Update map elements with leaflet proxy  
E.g. widget updates that don't refresh map each iteration 
<!-- https://www.youtube.com/watch?v=G5BDub -->

### Update map elements with hover
<!-- https://www.kaggle.com/skirmer/exploratory-analysis-of-austin-crime-with-maps -->

```{r}
require(maps)
require(leaflet)

# world.cities data from \maps
world_cities <- with(world.cities, data.frame(
  "city" = name,
  "country" = country.etc,
  "lat" = lat,
  "lon" = long,
  "population" = pop
  )
)
world_cities %>% str
latlon <- world_cities[,c("lat","lon")]
radius <- world_cities[,"population"]/1000000
popup <- world_cities[,"city"]
label <- world_cities[,"country"]

# style 
custom_tile <- "http://c.sm.mapstack.stamen.com/(toner-lite,(mapbox-water,$000[@80]),(parks,$000[@70]),(buildings,$fabe68[hsl-color]))/{z}/{x}/{y}.png"
colv <- "#F90F40"
opac <- 0.3

map <- leaflet() %>% 
  setView(0,0,zoom=3) %>% 
  addTiles(custom_tile) %>% 
  addCircleMarkers(latlon[,"lon"],
                   latlon[,"lat"],
                   radius = radius,
                   stroke = TRUE,
                   weight = 3, 
                   opacity = opac,
                   color = colv,
                   fillColor = colv,
                   label = label,
                   popup = popup 
  )
map

```

### Add minimap

<!-- https://rstudio.github.io/leaflet/morefeatures.html -->


### Add measurement tool

```{r}
# https://rstudio.github.io/leaflet/morefeatures.html
leaflet %>% 
  setview(0,0,13) %>% 
  addTiles(custom_tile) %>% 
  fitBounds(13.76134, 52.675499, 13.0884, 52.33812) %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479")
```


### Improve render performance with `leafgl`    
[https://github.com/r-spatial/leafgl](https://github.com/r-spatial/leafgl)   
```{r}

```

