---
title: My Google Timeline data with ` `r params$package` `   
author: |
 | Matthew Malishev  
 |  
 | @darwinanddavis  
 | 
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: blue
urlcolor: blue
citecolor: red
output:
  html_document:
    highlight: tango
    code_folding: show
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  package: "mapdeck"
  dir: "/Users/malishev/Documents/Data/gggmap"
  date: !r Sys.Date()
  session: !r sessionInfo()  
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/UsefulCode
classoption: portrait
# ^['https://github.com/darwinanddavis/UsefulCode'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
R version: `r params$version`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\  

R session info 

```{r, echo=F,aval=F}
params$session
```      

\newpage  

## Types of input data    

`sf`   
`geojson`  

## Overview

My Google timeline data with `r params$package`. 

**Need to export as HTML, then open in internet browser.**    

Install dependencies  
```{r, load packages, include=T, cache=F, message=F, warning=F, results='hide'}
packages <- c("pacman")   
if (require(packages)) {
    install.packages(packages,dependencies = T)
    require(packages)
}
lapply(packages,library,character.only=T)
p_load(dplyr,mapdeck,googleway)
```

Read in data  
```{r}
url <- url <- 'https://raw.githubusercontent.com/plotly/datasets/master/2011_february_aa_flight_paths.csv'
flights <- read.csv(url)
glimpse(flights)

# create new info vec for labels  
flights$info <- paste0("<b>",flights$airport1, " - ", flights$airport2, "</b>")
```

Have you already initiated the mapdeck gl?  
```{r}
usedmapkey <- 1 # 1 = init mapdeck function using mapkey once for each session, 0 = init again (for new r session or map)
```

Data inputs  
```{r}
my_data = flights
mapkey <- readLines("mb.txt") # read in your mapkey
set_token(mapkey) # set mapdeck globally for future sessions    
# create style #  https://studio.mapbox.com/
my_style <- "mapbox://styles/darwinanddavis/cjy1slolu144l1cr9407s5uep/draft" # draft style  
width <- 1000
height <- 1000
padding <- 0
pitch <- 75

radius <- 5
fill_colour <- "#5ED2DB"
highlight_colour <- "#CC000000" # needs to be hexcode with alpha prefix  
palette <- list(fill_colour = "magma") # see colourvalues::colour_palettes()
fill_opacity <- 20 # 0:255
auto_highlight <- T # highlight on hover
transitions <- list(position = 2000, fill_colour = 1000) # transitions take this form 
```

Set data inputs  
```{r}
# data 
# needs to be a col so create new cols with more appropriate names  
names(my_data)
my_data[,"lat"] <-  my_data[,"start_lat"]
my_data[,"lon"] <- my_data[,"start_lon"]
my_data[,"elevation"] <- sample(10000:10000000, size = nrow(my_data),replace=T) 
my_data[,"opacity"] <- sample(1:255, size = nrow(my_data),replace=T) 
id_point <- "point_1" # change with each layer
id_arc <- "arc_1" # change with each layer
id_poly <- "poly_1" # change with each layer
```

Plot  
```{r}
# plot --------------------------------------------------------------------
# save to html to view OR viewer > new window
if(usedmapkey==0){
  p <- mapdeck(my_data, 
               style = my_style,
               width = width,
               height = height,
               padding = padding,
               pitch = pitch)
}

# point cloud
p <- p %>% 
  add_pointcloud(lat = "lat", 
                 lon = "lon",
                 elevation = "elevation",
                 layer_id = id_point,
                 radius = radius, 
                 fill_colour = fill_colour,
                 fill_opacity = "opacity",
                 auto_highlight = auto_highlight, 
                 highlight_colour = highlight_colour,
                 tooltip = "info",
                 palette = palette,
                 update_view = T
                 # ---- extra stuff
                 # light_settings = light
                 # transitions = transitions
  )  
p
```


3D maps  

Run in normal R file, then export as HTML.   

```{r}
# produces mapdeck_working_20191229.html file 

# https://bookdown.org/robinlovelace/geocompr/adv-map.html
# @mapdeck
# install.packages("mapdeck")
# install.packages("usethis")

require(mapdeck)
require(usethis)
mb_key <- readLines("mb.txt")

set_token(Sys.getenv(mb_key))
df = read.csv("https://git.io/geocompr-mapdeck")
df <- df[ !is.na(df$lng ), ]
df <- df[ !is.na(df$lat ), ]

my_style = mapdeck_style("dark")
mapdeck(style = my_style, 
        token = mb_key, 
        pitch = 45, 
        location = c(0, 52), 
        zoom = 4) %>%
  add_grid(data = df, 
           lat = "lat", lon = "lng", 
           cell_size = 1000,
           elevation_scale = 50, 
           layer_id = "grid_layer",
           colour_range = viridisLite::plasma(6)
           )

```

