---
title: My Google Timeline data with ` `r params$package` `      
author: |
 | Matthew Malishev  
 |  
 | @darwinanddavis  
 | 
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
fontsize: 10
geometry: margin=1in
documentclass: article
linkcolor: blue
urlcolor: blue
citecolor: red
output:
  html_document:
    highlight: tango
    code_folding: show
    toc: yes
    toc_depth: 4
    number_sections: no
    toc_float: yes
  pdf_document:
    includes:
      in_header: # add .tex file with header content
    highlight: tango
    template: null
    toc: yes
    toc_depth: 4
    number_sections: false
    fig_width: 4
    fig_height: 5
    fig_caption: true
    df_print: tibble 
    citation_package: biblatex # natbib
    latex_engine: xelatex #pdflatex # lualatex
    keep_tex: true # keep .tex file in dir 
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: 
tags:
- nothing
- nothingness
params: 
  package: "googleway"
  dir: "/Users/malishev/Documents/Data/gggmap"
  date: !r Sys.Date()
  session: !r sessionInfo()  
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  doi: https://github.com/darwinanddavis/UsefulCode
classoption: portrait
# ^['https://github.com/darwinanddavis/UsefulCode'] # footnote
vignette: >
  %\VignetteIndexEntry{Useful R code}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, set-options, echo = FALSE, cache = FALSE}
options(width=100)
knitr::opts_chunk$set(
 eval = TRUE, # run all code
 # echo = FALSE, # show code chunks in output 
 comment = "",
 tidy.opts=list(width.cutoff=100), # set width of code chunks in output
 tidy=TRUE, # make output as tidy
 message = FALSE,  # mask all messages
 warning = FALSE, # mask all warnings 
 size="small" # set code chunk size
)

# https://github.com/ucb-stat133/stat133-fall-2016/blob/master/hws/hw02-tables-ggplot.Rmd
knitr::opts_knit$set(root.dir=paste0(params$dir,"/")) # set working dir

setwd(paste0(params$dir,"/")) # for running just in R not knitr
```

\newpage   

Date: `r params$date`  
R version: `r params$version`  
*Corresponding author: `r params$email`  
This document can be found at `r params$doi`  

\  

R session info 

```{r, echo=F,aval=F}
params$session
```      

\newpage  

## Overview

My Google timeline data with `r params$package`.   

**Need to export as HTML, then open in internet browser.**    

### Install dependencies
```{r, load packages, include=T, cache=F, message=F, warning=F, results='hide'}
packages <- c("rgdal","dplyr","zoo","RColorBrewer","viridis","plyr","digitize","jpeg","devtools","imager","dplyr","ggplot2","ggridges","ggjoy","ggthemes","svDialogs","data.table","tibble","extrafont","sp")   
if (require(packages)) {
    install.packages(packages,dependencies = T)
    require(packages)
}
lapply(packages,library,character.only=T)
```

## Getting distance between sites for future departure times  
<!-- #https://stackoverflow.com/questions/41850017/error-in-using-the-googlway-package-in-r -->
```{r}
# get developmental ver 
# devtools::install_github("SymbolixAU/googleway") # run once 
api_key <- readLines("ayepeeeye.txt") 

x <- as.POSIXct("2019-11-23 00:00:00", tz = "Europe/Paris")
get_dist <- google_distance(origins = list(c(48.93, 2.175)),
                                destinations =list(c(48.95, 2.19)),
                                mode="driving",
                                departure_time=x,
                                traffic_model='pessimistic',
                                key = api_key,
                                simplify = T)
get_dist 
```

